Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-23 analysis/paper/paper.Rmd
add paragraphs about OPP

>>>>

As we prepared this letter, we became more aware of the urgent need to spread and establish an open science attitude and culture among plant pathologists.
To assist in fostering this sort of change in our discipline, Open Plant Pathology (OPP), <https://www.openplantpathology.org>, an institution-independent and non-funded initiative, was founded in January 2018 by two of this letter's co-authors, Del Ponte and Sparks, in 2018 with the following vision: “foster a diverse community culture that values openness, transparency and reproducibility of scientific research data and methods in our field”.
We started OPP with a minimal infrastructure and support from other enthusiastic colleagues that allows members to interact sharing and gathering ideas on how we can improve the openness and reproducibility in our discipline.

We  believe that adopting an attitude of open and collaborative science and using the best reproducibility practices in our daily work, directly benefits us as researchers.

<!-- need to edit this portion
For example, between complicated analyses, reviews and revisions and questions years later about the data that was collected or analysis that was conducted, it is extremely beneficial to be able to easily reproduce your work quickly and easily.
Second, it is beneficial to the reviewer in understanding and providing suggestions for improvements when reviewing and the end-user or reader to be able to verify the validity of the methods used and recreate the analysis which helps with knowledge transfer.
Lastly, sharing work openly and making it discoverable can lead to new collaborations. 
end edit portion -->
